Doing Better Than UCT: \\ Rational Monte Carlo Sampling in Trees

### 2011-07-28 paper/rmcts/paper.tex
pdfs automatically

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-factor=_8438.pdf}
    {a. varying number of samples} 
 \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=8-nsamples=185.pdf}
    {b. varying exploration factor}
  \end{minipage}
  \caption{The sailing domain, a smaller lake}
  \label{fig:sailing-8}
\end{figure}

\begin{figure}[t]
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-factor=_5625.pdf}
    {a. varying number of samples}
  \end{minipage}
  \begin{minipage}[b]{0.5\linewidth} \centering
    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
    0pt,clip]{sailing-size=13-nsamples=240.pdf}
    {b. varying exploration factor}
  \end{minipage}
  \caption{The sailing domain, a larger lake}
  \label{fig:sailing-13}
\end{figure}

>>>>

%\begin{figure}[t]
%  \begin{minipage}[b]{0.5\linewidth} \centering
%    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
%    0pt,clip]{sailing-size=8-factor=_8438.pdf}
%    {a. varying number of samples} 
% \end{minipage}
%  \begin{minipage}[b]{0.5\linewidth} \centering
%    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
%    0pt,clip]{sailing-size=8-nsamples=185.pdf}
%    {b. varying exploration factor}
%  \end{minipage}
%  \caption{The sailing domain, a smaller lake}
%  \label{fig:sailing-8}
%\end{figure}
%
%\begin{figure}[t]
%  \begin{minipage}[b]{0.5\linewidth} \centering
%    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
%    0pt,clip]{sailing-size=13-factor=_5625.pdf}
%    {a. varying number of samples}
%  \end{minipage}
%  \begin{minipage}[b]{0.5\linewidth} \centering
%    \includegraphics[scale=0.45,trim=0pt 0pt 0pt
%    0pt,clip]{sailing-size=13-nsamples=240.pdf}
%    {b. varying exploration factor}
%  \end{minipage}
%  \caption{The sailing domain, a larger lake}
%  \label{fig:sailing-13}
%\end{figure}
